---
title: "goatea"
author: Maurits Unkel
output: 
  BiocStyle::html_document:
    toc: true
    toc_depth: 2
vignette: >
  %\VignetteIndexEntry{goatea}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
```

```{r library, echo = FALSE}
library(goatea)
```

TODO add introduction section (eval = FALSE)
Add an “Introduction” section that serves as an abstract to introduce the objective, models, unique functions, key points, etc that distinguish the package from other packages in the same area.
It should include a short motivation for the package in general as well as motivation for inclusion of the package in Biconductor. When relevant, a brief review and comparison of packages with similar functionality or scope should be provided either in the Introduction or in a separate dedicated vignette section.

TODO add installation section (eval = FALSE)
Add an “Installation” section that show to users how to download and load the package from Bioconductor.

TODO table of contents



```{r test}
print('test print')
```

```{r references, eval = FALSE}
GOAT package
Koopmans, F. GOAT: efficient and robust identification of gene set enrichment. Commun Biol 7, 744 (2024). https://doi.org/10.1038/s42003-024-06454-5
```

```{r end session info}
sessionInfo()
```